Instructions for running Shiny app to explore results of Gaussian mean estimation experiments

### 2018-12-18 analysis/gauss_shiny_setup.Rmd
Added link to Shiny package.

---
title: "Instructions for running Shiny server to explore results of Gaussian mean estimation experiments"
author: "Zhengrong Xing, Peter Carbonetto and Matthew Stephens"
output: workflowr::wflow_html
---

Here we give instructions for starting the Shiny server which will
create an interactive plot from the results of the Gaussian mean
estimation simulation study.

@@

Now you are ready to create the Shiny server with this command:

@@

>>>>

---
title: "Instructions for running Shiny app to explore results of Gaussian mean estimation experiments"
author: "Zhengrong Xing, Peter Carbonetto and Matthew Stephens"
output: workflowr::wflow_html
---

Here we give instructions for starting the [Shiny app][shiny] which
will create an interactive plot from the results of the Gaussian mean
estimation simulation study.

@@

Now you are ready to launch the Shiny app with this command:

@@

[shiny]: https://cran.r-project.org/package=shiny
